Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-26 paper/v1.0/sections/3_floquet_theory.tex
More corrections

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by Wackerl \textit{et al.} \cite{wackerl20}. In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field. Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

First we require to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}). By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be presented as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depended on a single quantum number ($n$). Then Floquet modes can be recognized as
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}. Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.

Then performing Fourier transform over the confined two-dimensional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we used new parameters
\begin{equation} \label{eq_11}
  b =
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
  d =
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For the detailed derivation please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

>>>>

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. As a method to analyze the transport properties of quantum systems exposed to strong radiation, the Floquet-Drude conductivity theory was introduced recently by Wackerl \textit{et al.} \cite{wackerl20}. In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field. Therefore, we are expecting to apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}). By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can present as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depend on a single quantum number $n$. Then Floquet modes are recognized as
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}. Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.

Then performing Fourier transform over the confined two-dimensional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we used new parameters
\begin{equation} \label{eq_11}
  b =
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
  d =
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For the detailed derivation, please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

### 2021-07-26 paper/v1.0/sections/4_inverse_scattering_time.tex
More corrections

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed disordered quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \times
    \int_{-\infty}^{\infty} d k_1 \Bigg[
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
  \end{aligned}
\end{equation}
where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix C. In this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results. Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} \equiv \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.

>>>>

The Floquet Fermi golden rule was proposed as a approach to analyze the transport properties in dressed quantum systems with impurities in Ref. \cite{wackerl20}. However, this theory has not been applied for a dressed quantum Hall system. In this study, we use Floquet Fermi golden rule to identify the effect induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for the inverse scattering time matrix ($(l,l')$-th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and x-directional momentum $k_x$ value for our considered quantum Hall system
\begin{equation} \label{eq_13}
  \begin{aligned}
    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
    & =
    \frac { \varrho^2}{eB}
    \delta(\varepsilon - \varepsilon_{N}) \\
    & \times
    \int_{-\infty}^{\infty} d k_1 \Bigg[
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
  \end{aligned}
\end{equation}
Here $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix \ref{appendix_c}. Since random impurities in a disordered metal is a better approximation for experimental results, in this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities.
Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}$.
Additionally, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
